### 2016-12-02 ms/hardcoded/ms.tex
version sent to ecol let

\documentclass[12pt]{article} 
\usepackage[pdftex]{graphicx}
\usepackage[numbers,sort&compress]{natbib} 
\usepackage{color}
\usepackage{amsmath} 
\usepackage{amssymb} 
\usepackage{verbatim}
\usepackage{mathpazo} 
\usepackage{setspace}
\usepackage{multirow}
\usepackage{fullpage}
\usepackage{lscape}
\usepackage{fancyhdr}
\usepackage[normalem]{ulem} 
\usepackage{hyperref}
\usepackage[parfill]{parskip}
\usepackage{xr}
\externaldocument{SI}
\usepackage{url}
\usepackage{rotating}

\hypersetup{colorlinks=true, linkcolor=black, citecolor=black}
\RequirePackage{lineno}

\newcommand{\flagged}[1] {
  \textcolor{blue}{#1}
}

@@

\def\runninghead{Plant-pollinator network assembly}
\def\keywords{community assembly, change points, robustness,
  nestedness, modularity, bipartite, preferential attachment}

\def\extras{
  \begin{itemize}
  \item Submitted as a Letter
  \item Abstract word count: 148
  \item Main text word count: 4967
  \item Number of references: 65
  \item Number of figures: 6
  \item Author contributions: CK designed the study, LCP and CK
    collected data, LCP and MPG analyzed output data.  LCP wrote the
    first draft of the manuscript, and all authors contributed to
    revisions.
  \item Data accessibility statement: Data will de depositied in Dryad
    upon publication
  \end{itemize}
}

@@

\begin{abstract}

Species are being lost at an alarming rate and it is imperative to understand how communities assemble if we are to prevent their collapse or restore lost interactions. We know little, however, about how to re-assemble interacting communities through restoration, or the process of ecological network assembly more generally. Using an eight-year dataset comprising nearly $20,000$ pollinator visitation records, we explore the assembly of plant-pollinator communities at native plant restorations sites in an agricultural landscape. We find that species occupy highly dynamic network positions through time, causing the assembly process to be punctuated by major network reorganizations. The most persistent and generalized species are also the most variable in their network positions, contrary to what assembly through preferential attachment predicts. Our results fundamentally alter our understanding of how communities assembly and how species interactions change through time while helping to inform efforts to re-assemble robust communities through restoration. %It was re-assembly but I think it is re-assemble no?

\end{abstract}

@@

%% introduce mutualisms, restoration, network assembly
%When a species goes extinct, more than a species is lost. That species
%interacted with other species in its community, likely in ways that
%were important or even crucial to others' survival. When a community
%--- a unique combination of interacting species --- loses one species,
%the system becomes weaker. 
Species in ecological communities are linked through ecological interactions. Global change, however, has created a severe
biodiversity crisis, and as species are lost, so are their
interactions \citep{dunn2009sixth, barnosky2011has}. A community's
ability to resist collapse will depend on the community's robustness to species and interaction loss \citep{Memmott2004, Rezende2007, Bascompte2009,
  Thebault2010}. Furthermore, it has been show that biodiversity has a pivotal role in maintaining ecosystems services \citep{cardinale-2012-59}. Thus, to safeguard ecological function, it has become
increasingly imperative to aid the recovery of lost interactions and
component biodiversity and by facilitating the assembly of robust
interaction networks via ecological restoration
\citep{menz-2010-4}. However, we know very little about how ecological
networks assemble in general, rendering restoration of interacting
communities quite difficult.

%% most people think network assemble via preferential attachment, and
%% there is some evidence of that. (other studies on mutualisms?)

@@

%% there are other ways to assemble that are not preferentia;
%% attchment, particularly vis big reorganizations of interactions
%% Lauren I love this paragraph!
In contrast to the network build-up described by preferential
attachment, significant reorganizations of interactions can also
punctuate assembly \citep{peel2014detecting}. Such significant
reorganizations of interactions, or network changing points, are
observed in social networks that respond to abrupt shifts in the
behavior of interactors \citep{peel2014detecting}. A change point is
caused by a merge, split, fragmentation or formation of modules within
a network. In ecological communities, such shifts may occur if, as new
species colonize, resident species change their interaction partners
to optimize their foraging effort. In plant-pollinator communities,
theory predicts that pollinators optimize their use of floral
resources to reduce interspecific competition and improve resource-use
efficiency \citep{pyke1984optimal, valdovinos2010consequences,
  valdovinos2013adaptive, albrecht2010plant, Bluthgen2007}. No
studies, however, have examined if network changing points occur
during ecological network assembly and/or how these changes relate to
species behavior.

%% restoration
Understanding network assembly is particularly relevant to ecological
restoration, which is essentially ``applied succession''
\citep[e.g.,][]{parker1997scale}.  In pollination systems, time has
been shown to affect the structure of networks in restored areas
\citep{forup-2008-742, devoto2012understanding}, suggesting that
interactions change as a community develops. Facilitating network
restoration is especially imperative in areas where species
interactions provide essential ecosystem services, such as crop
pollination in agricultural landscapes. To promote pollinator services
in agriculture, some farmers plant strips of native plants along farm
edges (hedgerows).  By providing habitat, hedgerows augment the
richness, abundance and trait diversity of pollinators in agricultural
landscapes \citep{morandin-2013-829, kremen-2015-602,
  ponisio2015farm}, and promote the persistence and colonization of
floral resource specialists \citep{mgonigle-2015-x}. As the community
assembles, it is important to understand how these new species are
incorporated into the network as well as the consequences of adding
species for interaction patterns and robustness.

%% Lauren I would put 10 year dataset; and I *loved* the way you
%% organized the ideas here!!
We explore the process of network development using a nine-year
dataset of plant-pollinator community assembly following hedgerow
restoration in the highly simplified and intensively managed
agricultural landscape of California’s Central Valley. We first
determine whether the mechanism underlying network assembly represents
a buildup of interactions as would be predicted by preferential
attachment or significant reorganizations of interactions (i.e.,
network changing points). Even with changing points in interaction
organization, networks could still assemble via preferential
attachment if the network reorganizations were primarily driven by
peripheral, temporally variable species while a stable, well-connected
core of species persist. Therefore, we tested whether the species that
are most variable in their network position --- and thus important
contributors to network reorganizations -- are less persistent and
connected species. To further explore the mechanisms underlying the
temporal dynamics of the networks, also we examine patterns in the
species and interaction temporal turnover. Finally, we investigate
whether networks assemble toward predictable interaction patterns, and
the ramifications for the robustness of the networks.

%% objectives
% 1) Are hedgerows assembling by preferential attachment, or are there
% more abrupt reorganizations of network structure?
% 2) Who are the species responsible for interaction reorganizations?
% how to incorporate this? 
% 3) Are the changing points a product of turnover in species
% composition, or are more substantial changes in the verticles of the
% networks?
% 4) Is the structure of interactions changing? Does this change the
% robustness of the network to species extinction and/or perturbation?

@@

Quantitative networks were generated for each site through
time. Because the nuber of sampling rounds varied between years
(Tables S1-S3), we used the mean of the interactions between a pair of
plants and pollinators within a year to represent interaction
frequency.

@@

Using Bayesian posterior inference and techniques from phylogenetic
tree reconstruction, we fit the GHRG model to the networks
\citep{peel2014detecting}. This is accomplished by using a Markov
chain Monte Carlo (MCMC) procedure to first sample the posterior
distribution of bipartitions, from which a consensus tree is derived
\citep{peel2014detecting}. We use $\beta$ distributions with the
hyperparameters $\alpha=\beta=1$ to define priors for $p_r$.

Once the GHRG model has been fit to the networks, we determine whether
a change point occurred between two time slices. To detect a change
point, we use Bayes factors to compare the fit of two models --- one
where a change point occurred between two networks, and one where no
change occurred. We chose a sliding window of length, $w$, of four
years to detect change points. Larger windows allow for more gradual
changes, and four was the maximum possible with our eight years of
data. Lastly, to calculate a $p$-value for the Bayes factors, we use
parametric bootstrapping to numerically estimate the null distribution
\citep{peel2014detecting}. We employed code published online by
L.~Peel for the change point analysis. Analyses were conducted in
Python 3.4.

@@

To further elucidate the nature of the change points, we examine the
characteristics of the species that contributed to interaction
reorganization. Some species remained in relatively similar network
positions through time, whereas others were more variable in their
position and thus contributed more strongly to network
reorganization. We tested whether the more persistent species with the
highest degree (number of different interaction partners) were the
most stable in their network positions, as would be expected if the
networks were assembling via preferential attachment.

We calculated species persistence as the proportion of surveys in
which a plant or pollinator is observed. Species observed consistently
within and between years were thus maximally persistent. Weighted
species degree is calculated from interaction observations from an
extensive dataset from Yolo County (approx.~18000 interaction records)
that included both the data included in this study and additional data
from sites where we collected flower visitors using the same methods
\citep{mgonigle-2015-x, ponisio2015farm}. To represent network
position variability, we computed the coefficient of variation of
weighted closeness centrality \citep{freeman1978centrality} at each
site through time. Closeness centrality represents the importance of a
space by calcuating the path lengths to other vertices (species) in
the network \citep{freeman1978centrality}. The shorter the mean path
length to other species, the higher the closeness centrality. We used
linear mixed models to test whether the species closeness variability
(log) is related to the persistence or degree of that species
\citep{lme4, lmetest}. We included random effects for species and
site. Because the degree and persistence of pollinators were strongly
correlated, ($\rho = 0.071$, $p$-value $<$ $2*10^{-16}$), we included
each explanatory variable in separate models. Plant degree and
persistence were not significantly correlated, but we used the same
models as we did for the pollinators for consistency.  Because an
approximately logarithmic increase in closeness centrality --- as
would be expected with assembly by preferential attachment --- we also
tested whether log closeness centrality increases through time.

@@

%%Lauren I really liked the way you explained this part =]
Reorganizations of network structure can be the result of species
turnover or species changing their interaction partners (i.e.,
re-wiring). To better understand the mechanisms underlying the
temporal dynamics of the assembling networks, we examined patterns of
species and interaction turnover. For example, assembling networks may
have higher rates of pollinator turnover than non-assembling
communities because new pollinator species are colonizing and
establishing themselves \citep{mgonigle-2015-x}. Similarly, because
species are turning over and pollinators are trying to maximize their
foraging efficiency based on the species present, interactions may
turnover more quickly than in established communities. In addition, at
assembling hedgerows, plants that are unvisited in early years may
appear to ``colonize'' the networks as they became more attractive
resources and establish new interactions with pollinators.

@@

Though species may turnover across years, some groups of species may
essentially replace each other if they fill similar roles in the
network, occupying the same network position and interacting with
similar species. At non-assembling communities, species turnover may
overestimate the temporal changes in the networks if the interactions
occurring in one year are similar to those in the next year when they
are weighted by the similarity of their constituent species
(Fig.~\ref{fig:methods}). We developed a method to examine the
temporal turnover of interactions with weightings based on their
similarity. We followed the algorithm of \cite{ahn2010link} to cluster
all the interactions (edges) hierarchically across sites and years
based on their similarity, and build a dendrogram. The interaction
similarity is based how many plants and pollinators (vertices) two
edges share \citep{ahn2010link, kalinka2011linkcomm}. The more species
edges shared in common, the shorter the branch length between them on
the dendrogram.  We next calculated the temporal turnover of
interactions weighted by their similarity, as approximated by
``phylogenetic'' distance \citep{graham2008phylogenetic,
  picante-2010-1463}. We then used linear mixed models to test whether
the weighted turnover of interactions varied between assembling and
non-assembling networks, including site as a random effect
\citep{lme4, lmetest}.

@@

\subsection*{Network structure}
Any changing points in network structure may contribute to the
reorganization of the assembling networks into predictable interaction
patterns. Pollination networks exhibit two main structural patterns
--- modularity \citep[e.g.,][]{Olesen2007} and nestedness
\citep[e.g.,][]{Bascompte2006, Bascompte2003}. In modular networks,
interactions are insular, occurring within separate groups or
``modules'' more often than between modules. Modules in the network
may fragment as the network assembles, enhancing
modularity. Conversely, nested networks are like a pyramid of
interactions, where there are some species that interact with many
species, other species that interact with a subset of those species,
and so on. If species entering the network tend to interact with the
generalist base of the network pyramid as would be expected with
preferential attachment, nestedness would increase through time. The
connectance --- the proportion of observed out of possible
interactions --- would decrease as new, specialist species,
preferentially attach to the core. Finally, the overall level of
network specialization may change as the community
assembles. Network-level specialization will increase if specialist
species colonize the network or species begin to limit their
interaction niche breath as the network assembles
\citep{bluthgen-2006-9}.

To evaluate network nestedness, we used the estimator weighted NODF
\citep{almeida-neto-2008-1227}. NODF evaluates whether species with
fewer partners interact with subsets of partners with which more
connected species interact \citep{almeida-neto-2008-1227}. To estimate
modularity, we used a hierarchical clustering algorithm
\citep{Newman2004, csardi-2006}. We evaluate network specialization with
the metric H2, which estimates the deviation of the observed
interaction frequency between plants and pollinators from a null
expectation where all partners interact in proportion to their
abundances \citep{bluthgen-2006-9}. It ranges from zero for
generalized networks to one for specialized networks.  We calculated
standardized $z$-scores so that nestedness, modularity and
specialization metrics could be compared across communities. The
$z$-scores were calculated by generating an ensemble of $999$ randomly
assembled communities, subtracting the mean of the statistic
calculated across these communities from the observed value, and then
dividing by the standard deviation. To assemble random communities, we
reshuffled the interactions between species but fixed the total number
of interactions, species and interaction frequency distributions
\citep{Galeano2009}.

To test whether network modularity, nestedness, connectance or
specialization changed linearly with assembly, we usedd linear mixed
models with the descriptive network metrics as the response variable,
year of assembly as the explanatory variable, and random effects of
site and year. The number of species in a network affects the patterns
of interaction possible, so we also examined the change in plant and
pollinator species richness through time. We employ generalized linear
mixed models with Poisson error to model richness \citep{lme4}. We
scaled explanatory variables.

\subsection*{Network robustness}
Lastly, we tested whether the changes in interaction patterns
associated with network assembly affect the robustness of the network
to species loss and cascading perturbations. Following
\cite{Memmott2004}, we simulated plant species extinction and the
subsequent extinction cascades of pollinator species. Becaused the
reproduction of plant species is facilitated by active restoration
efforts, it is unlikely the extinction of pollinator species would
affect plant populations in the hedgerows. However, plants ceasing to
bloom, for example in response to drought, will likely affect the
pollinators that depend on them. We eliminated plants species based on
their degree or abundance, and then calculated the number of
pollinators that secondarily went extinct. The area below the
extinction curve is an estimate of network robustness
\citep{Memmott2004, bipartite}.

We also explored how the robustness to cascading perturbations changed
as the community assembled, using algebraic connectivity --- the
second smallest eigenvalue of the Laplacian matrix
\citep{fiedler1973algebraic} --- as a proxy for network robustness.
% (Gaiarsa et al., in prep)
Algebraic connectivity relates to how difficult it is to turn a
network into completely disconnected groups of species
\citep{costa2007characterization, gibert2013spatial}. The larger the
algebraic connectivity, the more sensitive a network is to cascading
perturbations. Perturbations, such as the decrease in abundance of a
plant or pollinator, can have negative consequences for the species in
the network. For example, a decrease in abundance of a pollinator will
diminish the pollination services it provides to plants. The affected
plants would set less seeds, and decrease in abundance the subsequent
year. Consequently, other pollinators that depended on those plant
species would also be affected, and the effects of this perturbation
would continue to propagate throughout the network. Alternatively,
perturbations could also have a positive effect if, for example, the
increase in the abundance of a plant species lead to an increase in
resource availability for pollinators. The examples of negative
perturbations (e.g., resource collapse, disease spreading, parasites),
however, outnumber possible positive perturbations. It is important to
note that both robustness and algebraic connectivity assume that the
network is static. They do not account for the ability of species to
alter their interaction depending on circumstances and the resource
availability.

@@

In contradiction to the predictions of assembly by preferential
attachment, both pollinator persistence and degree were positively
related to network position variability (Fig.~\ref{fig:cv}, estimate
of the slope of closeness centrality variability and persistence $\pm$
standard error of the estimate, $0.496 \pm 0.182$, $p$-value=$0.016$;
slope of closeness centrality variability and degree, $0.004 \pm
0.002$, $p$-value=$0.056$). The slope of these relationships remained
significant when the species with the top $10$ persistence and degree
scores were dropped. In addition, plant persistence and degree were
not significantly related to network position variability
(Fig.~\ref{fig:cv}). % estimate of the slope of closeness variability and
% persistence $\pm$ SE, $-2.063 \pm 3.091$, $p$-value=$0.5$; slope of
% closeness variability and degree, $0.0018 \pm 0.002$,
% $p$-value=$0.3$).
The variability of species network position was not the result of
closeness linearly increasing through time, and, in fact, plant and
pollinator closeness decreased slightly through time (Fig.~S2,
estimate of the slope of closeness through time $\pm$ SE, pollinators:
$-0.082 \pm 0.021$, $p$-value=$0.003$; plants $-0.089 \pm 0.044$,
$p$-value=$0.04$).

@@

\section*{Temporal changes in interaction patterns}
\subsection*{Network structure}
%Network nestedness significantly increased with assembly
%(Fig.~\ref{fig:baci}, estimate of the slope of nestedness through time
%$\pm$ SE, $1.834 \pm 0.6142$, $p$-value=$0.022$). 
Nestedness and modularity did not change in any predictable pattern
with assembly (Fig.~\ref{fig:baci}). All of the networks were
significantly nested ($z$-scores $>$ $1.96$), but not modular ($z$-scores
$<$ 2, Fig.~\ref{fig:baci}).

%though the slope was not significantly different from
%zero.(estimate
% of the slope of modularity through time $\pm$ standard error of the
% estimate, $-0.524$ $\pm$ $0.295$, $p$-value=$0.124$).
%In addition, none of the networks were significantly modular
% Fig.~\ref{fig:baci}).

Connectance decreased as the community assembled (Fig.~\ref{fig:baci},
estimate of the slope of connectance through time $\pm$ standard error
of the estimate, $-0.023$ $\pm$ $0.008$,
$p$-value=$0.007$). Specialization also decreased, though the slope
was not significantly different from
zero. %(estimate of the slope of specialization through time $\pm$ SE, $-0.926$ $\pm$ $0.450$, $p$-value=$0.078$).
Most communities were more generalized than expected when interactions
were randomized (Fig.~\ref{fig:baci}).

@@

\subsection*{Network robustness}
Assembly did not affect network robustness to species
extinction when species were removed incrementally by
degree or abundance % (estimate
% of the slope of robustness through time $\pm$ SE, $6*10^{-5} \pm
% 4*10^{-3}$, $p$-value=$0.987$) ($0.001 \pm 0.003$,
% $p$-value=$0.65$)
In contrast, the sensitivity of networks to cascading perturbations,
as measured by the algebraic connectivity of the network, increased as
the network assembled (Fig.~S3), estimate of the slope of
sensitivity to cascading perturbations through time $\pm$ SE, $0.6814
\pm 0.272$, $p$-value=$0.042$).

@@

When we explored how network-level interaction patterns changed
through time, we found few patterns. The connectance decreased, as
would be expected if the network is being colonized by specialist
species \citep{mgonigle-2015-x}. Network specialization, however, did
not change predictably with assembly. Decreasing connectance without
an accompanying increase in specialization would be possible if the
increased colonization of specialized species was accompanied by an
increase in the diet breath of resident species. This would be
expected if resident species were able to minimize their foraging time
by expanding their diet breath as plant diversity increases with
hedgerow maturation \citep{Waser1996, pyke1984optimal, Bluthgen2007,
  albrecht2010plant}.

>>>>

\documentclass[12pt]{article}
\usepackage[pdftex]{graphicx}
\usepackage[numbers]{natbib}
% \usepackage{natbib}
\usepackage{color}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{verbatim}
\usepackage{mathpazo}
\usepackage{setspace}
\usepackage{multirow}
\usepackage{fullpage}
\usepackage{lscape}
\usepackage{array}
\usepackage{paralist}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{times}
\usepackage{textcomp}
\usepackage{xr}
\usepackage{etoolbox}
\usepackage{filecontents}
\usepackage{url}
\usepackage{rotating}
\externaldocument{SI}

\makeatletter
\def\@biblabel#1{#1.\\}
\makeatother

\parindent=2em
\setlength{\parskip}{1ex}

\RequirePackage{lineno}

@@

\def\runninghead{Plant-pollinator network assembly}
\def\keywords{community assembly, change points, robustness,
  nestedness, modularity, restoration, mutualism, preferential attachment}

\def\extras{
  \begin{itemize}
  \item Submitted as a Letter
  \item Abstract word count: 136
  \item Main text word count: 4680
  \item Number of references: 67
  \item Number of figures: 6
  \item Author contributions: CK designed the study, LCP and CK
    collected data, LCP and MPG analyzed output data.  LCP wrote the
    first draft of the manuscript, and all authors contributed to
    revisions.
  \item Data accessibility statement: Data will de depositied in Dryad
    upon publication
  \end{itemize}
}

@@

\begin{abstract}  
  Species and interactions are being lost at alarming rates and it is
  imperative to understand how communities assemble if we are to
  prevent their collapse and restore lost interactions. Using an
  eight-year dataset comprising nearly $20,000$ pollinator visitation
  records, we explore the assembly of plant-pollinator communities at
  native plant restorations sites in an agricultural landscape. We
  find that species occupy highly dynamic network positions through
  time, causing the assembly process to be punctuated by major network
  reorganizations. The most persistent and generalized pollinator
  species are also the most variable in their network positions,
  contrary to what preferential attachment --- the most widely studied
  theory of network assembly --- predicts. Our results fundamentally
  alter our understanding of how communities assembly and how species
  interactions change through time while helping to inform efforts to
  re-assemble robust communities through restoration.
\end{abstract}

@@

Species in ecological communities are linked through ecological
interactions. As the world continues to lose species at an alarming
rate \citep{dunn2009sixth, barnosky2011has}, anticipating a
community's ability to resist collapse will depend on the strength of
each interaction network and the species within it \citep{Memmott2004,
  Rezende2007, Bascompte2009, Thebault2010}. Furthermore, it has been
show that biodiversity has a pivotal role in maintaining ecosystems
services \citep{cardinale-2012-59}. Thus, to safeguard ecological
function, it has become increasingly imperative to aid the recovery of
lost interactions and component biodiversity and by facilitating the
assembly of robust interaction networks via ecological restoration
\citep{menz-2010-4}. However, we know very little about how ecological
networks assemble in general, rendering restoration of interacting
communities quite difficult.

@@

Significant reorganizations of interactions --- change points --- can
also punctuate assembly \citep{peel2014detecting}. A change point is
caused by a merge, split, fragmentation or formation of modules within
a network. Such interaction reorganizations are observed in social
networks responding to abrupt shifts in the behavior of interactors
\citep{peel2014detecting}. In ecological communities, such shifts may
occur if, as new species colonize, resident species change their
interaction partners to optimize their foraging effort
\citep{pyke1984optimal, Bluthgen2007, valdovinos2010consequences,
  albrecht2010plant, valdovinos2013adaptive}. For preferential
attachment to be at play, change points would need to be driven
primarily by peripheral, temporally variable species while a stable,
well-connected core of species remained stable in their
interactions. No studies, however, have examined if network changing
points occur during ecological network assembly and/or how these
changes relate to species behavior.

Understanding network assembly is particularly relevant to ecological
restoration, which is essentially ``applied succession''
\citep[e.g.,][]{parker1997scale}.  In pollination systems, time has
been shown to affect the structure of networks in restored areas
\citep{forup-2008-742, devoto2012understanding}, suggesting that
interactions change as a community develops. Facilitating network
restoration is especially imperative in areas where species
interactions provide essential ecosystem services, such as crop
pollination in agricultural landscapes. To promote pollinator services
in agriculture, some farmers plant strips of native plants along farm
edges (hedgerows).  By providing habitat, hedgerows augment the
richness, abundance and trait diversity of pollinators in agricultural
landscapes \citep{morandin-2013-829, kremen-2015-602,
  ponisio2015farm}, and promote the persistence and colonization of
floral resource specialists \citep{mgonigle-2015-x}. As the community
assembles, it is important to understand how these new species are
incorporated into the network as well as the consequences of adding
species for interaction patterns and robustness.

We explore the process of network development using a eight-year
dataset of plant-pollinator community assembly following hedgerow
installment in the highly simplified and intensively managed
agricultural landscape of California's Central Valley. We first
determine whether network assembly was punctuated by significant
reorganizations of interactions. We next tested whether the species
that are most variable in their network position --- and thus
important contributors to network reorganizations --- are less
persistent and connected species, as would be expected by preferential
attachment. To further explore the mechanisms underlying the temporal
dynamics of the networks, also we examine patterns in the species and
interaction temporal turnover. Finally, we investigate whether
networks assemble toward predictable interaction patterns, and the
ramifications for the robustness of the networks.

@@

Quantitative networks were generated for each site through
time. Because the number of sampling rounds varied between years
(Tables S1-S3), we used the mean of the interactions between a pair of
plants and pollinators within a year to represent interaction
frequency.

@@

Using Bayesian posterior inference and techniques from phylogenetic
tree reconstruction, we fit the GHRG model to the networks
\citep{peel2014detecting}. We used a Markov chain Monte Carlo (MCMC)
procedure to first sample the posterior distribution of bipartitions,
from which a consensus tree was derived \citep{peel2014detecting}. We
used $\beta$ distributions with the hyperparameters $\alpha=\beta=1$
to define priors for $p_r$.

Once the GHRG model was fit to the networks, we determined whether a
change point occurred between two time slices. To detect a change
point, we used Bayes factors to compare the fit of two models --- one
where a change point occurred between two networks, and one where no
change occurred. We chose a sliding window of length, $w$, of four
years to detect change points. Larger windows allow for more gradual
changes, and four was the maximum possible with our eight years of
data. Lastly, to calculate a $p$-value for the Bayes factors, we used
parametric bootstrapping to numerically estimate the null distribution
\citep{peel2014detecting}. We employed code published online by
L.~Peel for the change point analysis. Analyses were conducted in
Python 3.4.

@@

To further elucidate the nature of the change points, we examined the
characteristics of the species that contributed to interaction
reorganization. We tested whether the more persistent species with the
highest degree (number of different interaction partners) were the
most stable in their network positions, as would be expected if the
networks were assembling via preferential attachment.

We calculated species persistence as the proportion of surveys in
which a plant or pollinator is observed. Species observed consistently
within and between years were thus maximally persistent. Species
degree was calculated from interaction observations from an extensive
dataset from Yolo County (approx.~18000 interaction records) that
included both the data included in this study and additional data from
sites where we collected flower visitors using the same methods
\citep{mgonigle-2015-x, ponisio2015farm}. To represent network
position variability, we computed the coefficient of variation of
weighted closeness centrality \citep{freeman1978centrality} at each
site through time. Closeness centrality represents the importance of a
species by calculating the path lengths to other vertices (species) in
the network \citep{freeman1978centrality}. The shorter the mean path
length to other species, the higher the closeness centrality. We used
linear mixed models to test whether the species closeness variability
(log) is related to the persistence or degree of that species
\citep{lme4, lmetest}. We included random effects for species and
site. Because the degree and persistence of pollinators were strongly
correlated, ($\rho = 0.071$, $p$-value $<$ $2*10^{-16}$), we included
each explanatory variable in separate models. Plant degree and
persistence were not significantly correlated, but we used the same
models as we did for the pollinators for consistency.  Because an
approximately logarithmic increase in closeness centrality --- as
would be expected with assembly by preferential attachment --- we also
tested whether log closeness centrality increased through time.

@@

Reorganizations of network structure can be the result of species
turnover or species changing their interaction partners (i.e.,
re-wiring). To better understand the mechanisms underlying the
temporal dynamics of the assembling networks, we examined patterns of
species and interaction turnover. For example, assembling networks may
have higher rates of pollinator turnover than non-assembling
communities because new pollinator species are colonizing and
establishing themselves \citep{mgonigle-2015-x}. Similarly, because
species are turning over and pollinators are trying to maximize their
foraging efficiency based on the species present, interactions may
turnover more quickly than in established communities. In addition, at
assembling hedgerows, plants that are unvisited in early years may
appear to ``colonize'' the networks as they became more attractive
resources and establish new interactions with pollinators.

@@

Though species may turnover across years, some groups of species may
essentially replace each other if they fill similar roles in the
network, occupying the same network position and interacting with
similar species. At non-assembling communities, species turnover may
overestimate the temporal changes in the networks if the interactions
occurring in one year are similar to those in the next year when they
are weighted by the similarity of their constituent species
(Fig.~\ref{fig:methods}). We developed a method to examine the
temporal turnover of interactions with weightings based on their
similarity. We followed the algorithm of \cite{ahn2010link} to cluster
all the interactions (edges) hierarchically across sites and years
based on their similarity, and built a dendrogram. The interaction
similarity is based how many plants and pollinators (vertices) two
edges share \citep{ahn2010link, kalinka2011linkcomm}. The more species
edges shared in common, the shorter the branch length between them on
the dendrogram.  We next calculated the temporal turnover of
interactions weighted by their similarity, as approximated by
``phylogenetic'' distance \citep{graham2008phylogenetic,
  picante-2010-1463}. We then used linear mixed models to test whether
the weighted turnover of interactions varied between assembling and
non-assembling networks, including site as a random effect
\citep{lme4, lmetest}.

@@

\subsection*{Network structure}
Any changing points in network structure may contribute to the
reorganization of the assembling networks into predictable interaction
patterns. Pollination networks exhibit two main structural patterns
--- modularity \citep[e.g.,][]{Olesen2007} and nestedness
\citep[e.g.,][]{Bascompte2006, Bascompte2003}. In modular networks,
interactions are insular, occurring within separate groups or
``modules'' more often than between modules. Modules in the network
may fragment as the network assembles, enhancing
modularity. Conversely, nested networks are like a pyramid of
interactions, where there are some species that interact with many
species, other species that interact with a subset of those species,
and so on. If species entering the network tend to interact with the
generalist base of the network pyramid as would be expected with
preferential attachment, nestedness would increase through time. The
connectance --- the proportion of observed out of possible
interactions --- would also decrease as new, specialist species,
preferentially attach to the core. Finally, network-level
specialization will increase if specialist species colonize the
network or species begin to limit their interaction niche breath as
the network assembles \citep{bluthgen-2006-9}.

To evaluate network nestedness, we used the estimator weighted NODF
\citep{almeida-neto-2008-1227}. NODF evaluates whether species with
fewer partners interact with subsets of partners with which more
connected species interact \citep{almeida-neto-2008-1227}. To estimate
modularity, we used a hierarchical clustering algorithm
\citep{Newman2004, csardi-2006}. We evaluated network specialization
with the metric H2, which estimates the deviation of the observed
interaction frequency between plants and pollinators from a null
expectation where all partners interact in proportion to their
abundances \citep{bluthgen-2006-9}. It ranges from zero for
generalized networks to one for specialized networks.  We calculated
standardized $z$-scores so that nestedness, modularity and
specialization metrics could be compared across communities. The
$z$-scores were calculated by generating an ensemble of $999$ randomly
assembled communities, subtracting the mean of the statistic
calculated across these communities from the observed value, and then
dividing by the standard deviation. To assemble random communities, we
reshuffled the interactions between species but fixed the total number
of interactions, species and interaction frequency distributions
\citep{Galeano2009}.

To test whether network modularity, nestedness, connectance or
specialization changed linearly with assembly, we used linear mixed
models with the descriptive network metrics as the response variable,
year of assembly as the explanatory variable, and random effects of
site and year. The number of species in a network affects the patterns
of interaction possible, so we also examined the change in plant and
pollinator species richness through time. We employed generalized
linear mixed models with Poisson error to model richness
\citep{lme4}. We scaled explanatory variables.

\subsection*{Network robustness}
Finally, we tested whether the changes in interaction patterns
associated with network assembly affect the robustness of the network
to species loss and cascading perturbations. Following
\cite{Memmott2004}, we simulated plant species extinction and the
subsequent extinction cascades of pollinator species. Because the
reproduction of plant species is facilitated by active restoration
efforts, it is unlikely the extinction of pollinator species would
affect plant populations in the hedgerows. However, plants ceasing to
bloom, for example in response to drought, will likely affect the
pollinators that depend on them. We eliminated plants species based on
their degree or abundance, and then calculated the number of
pollinators that secondarily went extinct. The area below the
extinction curve is an estimate of network robustness
\citep{Memmott2004, Burgos2007, bipartite}.

We also explored how the robustness to cascading perturbations changed
as the community assembled, using algebraic connectivity --- the
second smallest eigenvalue of the Laplacian matrix
\citep{fiedler1973algebraic} --- as a proxy for network robustness.
Algebraic connectivity relates to how difficult it is to turn a
network into completely disconnected groups of species
\citep{costa2007characterization, gibert2013spatial}. The larger the
algebraic connectivity, the more sensitive a network is to cascading
perturbations. Perturbations, such as the decrease in abundance of a
plant or pollinator, can have negative consequences for the species in
the network. For example, a decrease in abundance of a pollinator will
diminish the pollination services it provides to plants. The affected
plants would set less seeds, and decrease in abundance the subsequent
year. Consequently, other pollinators that depended on those plant
species would also be affected, and the effects of this perturbation
would continue to propagate throughout the network. Alternatively,
perturbations could also have a positive effect if, for example, the
increase in the abundance of a plant species lead to an increase in
resource availability for pollinators. The examples of negative
perturbations (e.g., resource collapse, disease spreading, parasites),
however, outnumber possible positive perturbations. It is important to
note that both robustness and algebraic connectivity assume that the
network is static --- they do not account for the ability of species
to alter their interaction depending on circumstances and the resource
availability.

@@

In contradiction to the predictions of assembly by preferential
attachment, both pollinator persistence and degree were positively
related to network position variability (Fig.~\ref{fig:cv}, estimate
of the slope of closeness centrality variability and persistence $\pm$
standard error of the estimate, $0.496 \pm 0.182$, $p$-value=$0.016$;
slope of closeness centrality variability and degree, $0.004 \pm
0.002$, $p$-value=$0.056$). The slope of these relationships remained
significant when the species with the top $10$ persistence and degree
scores were dropped. In addition, plant persistence and degree were
not significantly related to network position variability
(Fig.~\ref{fig:cv}).  The variability of species network position was
not the result of closeness linearly increasing through time, and, in
fact, plant and pollinator closeness decreased slightly through time
(Fig.~S2, estimate of the slope of closeness through time $\pm$ SE,
pollinators: $-0.082 \pm 0.021$, $p$-value=$0.003$; plants $-0.089 \pm
0.044$, $p$-value=$0.04$).

@@

\section*{Temporal changes in interaction patterns}
\subsection*{Network structure}

Nestedness, modularity and specialization did not change predictably
assembly (Fig.~\ref{fig:baci}). All of the networks were significantly
nested ($z$-scores $>$ $2$), but not modular ($z$-scores $<$ 2,
Fig.~\ref{fig:baci}). Most communities were more generalized than
expected when interactions were randomized
(Fig.~\ref{fig:baci}). Connectance decreased as the community
assembled (Fig.~\ref{fig:baci}, estimate of the slope of connectance
through time $\pm$ standard error of the estimate, $-0.023$ $\pm$
$0.008$, $p$-value=$0.007$).

@@

\subsection*{Network robustness}
Assembly did not affect network robustness to species extinction when
species were removed incrementally by degree or abundance
(Fig.~S3). Similarly, the sensitivity of networks to cascading
perturbations, as measured by the algebraic connectivity of the
network, did not change predictably as the community assembled
(Fig.~S3).

@@

When we explored how network-level interaction patterns changed
through time, we found few patterns. The connectance decreased, as
would be expected if the network is being colonized by specialist
species \citep{mgonigle-2015-x}. Network specialization, however, did
not change predictably with assembly. Decreasing connectance without
an accompanying increase in specialization would be possible if the
increased colonization of specialized species was accompanied by an
increase in the diet breath of resident species. This would be
expected if resident species were able to minimize their foraging time
by expanding their diet breath as plant diversity increases with
hedgerow maturation \citep{pyke1984optimal, Waser1996, Bluthgen2007,
  albrecht2010plant}.
